Data_Import

### 2023-04-03 Data_Import.Rmd
Deleted depression stuff from the inport file

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
## long / wide data
library(tidyr)
```

## Import data
Read in the dataset. 
```{r}
df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
view(df)
Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
```
## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles

@@

```{r}
### Bar Chart for Discharge Status ###
plot(Mothership2$DC_status_1)

@@

## Depression Treatment Progress Charts

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Depression Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL) +
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = 34, label = "Q1") +
  annotate("text", x = 8, y = 34, label = "Mean") +
  annotate("text", x = 13, y = 34, label = "Q3")

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20)) +
  labs(
    title="Quantity of discharges Per Treatment Day")

### plot means based upon duration group membership 
```{r}
ggplot(Mothership, aes(x = Duration, y = Days_complete_1)) +
  geom_violin()+
  geom_boxplot(width=0.1, color="blue", alpha=0.2)

Mothership_duration_CUDOS<-Mothership_Long %>%
  group_by(TxDay,Duration) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

```{r}
#plot depression mean with each group

Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUDOS[6:20,3] = NA
Mothership_duration_CUDOS[37:41,3] = NA
Mothership_duration_CUDOS[74:83,3] = NA
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
Mothership_duration_CUDOS

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3")

>>>>

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

## Import data
Read in the dataset. 
```{r}
df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
#view(df)
Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
```
## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles

@@

## Export as CSV
```{r}
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Vis.csv")
```

# Background Statistics
```{r}
### Bar Chart for Discharge Status ###
plot(Mothership2$DC_status_1)

@@
